### 2022-07-20 draft.tex
Deploying to gh-pages from @ FrancisBanville/ms_maxent_networks@ce1bc28dd8ef4504c2c64d28c93cd48ccae6af91 🚀

The flexible links model is a generative model, i.e.~it can generate
plausible values of the predicted variable. We thus simulated \(1000\)
values of \(L\) for different values of \(S\) using the joint posterior
distribution of our model parameters eq.~\ref{eq:BBpost}, and calculated
the mean degree for each simulated values. The resulting distributions
are shown in the left panel of fig.~\ref{fig:degree_dist_fl} for three
different values of species richness. In the right panel of
fig.~\ref{fig:degree_dist_fl}, we show how the probability distribution
for the mean degree constraints can be used to generate a distribution
of maximum entropy degree distributions, since each simulated value of
mean degree generates a different maximum entropy degree distribution
eq.~\ref{eq:lagrange_dd}.

\begin{figure}
\hypertarget{fig:degree_dist_fl}{%
\centering
\includegraphics{figures/maxent_degree_dist_fl.png}
\caption{(a) Probability density of the predicted mean degree for
different values of species richness. The number of interactions was
predicted using the flexible links model fitted to all empirical
networks in our complete dataset eq.~\ref{eq:BBpost}. (b) Degree
distributions of maximum entropy for a network of \(S=27\) species and
different numbers of interactions \(L\). The numbers of interactions
correspond to the lower and upper bounds of the \(67%
\), \(89%
\), and \(97%
\) percentile intervals (PI), as well as the median (in blue), of the
counterfactuals of the flexible links model. Each degree distribution
was obtained using eq.~\ref{eq:lagrange_dd} after solving numerically
eq.~\ref{eq:lagrange2_dd} using different values for the mean degree
constraint \(2L/S\).}\label{fig:degree_dist_fl}
}
\end{figure}

>>>>

The flexible links model is a generative model, i.e.~it can generate
plausible values of the predicted variable. We thus simulated \(1000\)
values of \(L\) for different values of \(S\) using the joint posterior
distribution of our model parameters (eq.~\ref{eq:BBpost}), and
calculated the mean degree for each simulated values. The resulting
distributions are shown in the left panel of
fig.~\ref{fig:degree_dist_fl} for three different values of species
richness. In the right panel of fig.~\ref{fig:degree_dist_fl}, we show
how the probability distribution for the mean degree constraints can be
used to generate a distribution of maximum entropy degree distributions,
since each simulated value of mean degree generates a different maximum
entropy degree distribution (eq.~\ref{eq:lagrange_dd} and
eq.~\ref{eq:lagrange2_dd}).

\begin{figure}
\hypertarget{fig:degree_dist_fl}{%
\centering
\includegraphics{figures/maxent_degree_dist_fl.png}
\caption{(a) Probability density of the predicted mean degree for
different values of species richness. The number of interactions was
predicted using the flexible links model fitted to all empirical
networks in our complete dataset (eq.~\ref{eq:BBpost}). (b) Degree
distributions of maximum entropy for a network of \(S=27\) species and
different numbers of interactions \(L\). The numbers of interactions
correspond to the lower and upper bounds of the \(67%
\), \(89%
\), and \(97%
\) percentile intervals (PI), as well as the median (in blue), of the
counterfactuals of the flexible links model. Each degree distribution
was obtained using eq.~\ref{eq:lagrange_dd} after solving numerically
eq.~\ref{eq:lagrange2_dd} using different values for the mean degree
constraint \(2L/S\).}\label{fig:degree_dist_fl}
}
\end{figure}
